---
title: "Effects of monetary policy shocks on exchange rate: Evidence from Australia"
author: "Yufei Wu"

execute:
  echo: false
  
bibliography: references.bib
---

> **Abstract.** This research proposal aim to examine the exchange rate reactions to monetary policy shocks in Australia from 1980 to 2022 using the Bayesian Structural Vector Auto-regression (SVAR) model.
>
> **Keywords.**  R, Monetary policy, exchange rate, SVAR model

# Introduction

This is a template repository for the Research Report for **Macroeconometrics**. Learn more about about developing online reports with **quarto** at [quarto.org](https://quarto.org/).


# Data

```{r}
#| label: load-packages
#| include: false
library(patchwork)
library(readrba)
library(xts)
library(ggplot2)
library(readabs)
```

```{r}
#| echo: false
#| message: false
exchange_rate_usd <- read_rba(series_id = "FXRUSD") 

exchange_rate_usd = xts(as.numeric(exchange_rate_usd$value), order.by = exchange_rate_usd$date) 
exchange_rate_usd <- to.quarterly(exchange_rate_usd,OHLC = FALSE)

exchange_rate_usd <- window(exchange_rate_usd,                   
                    start = "1980 Q1",
                    end = "2022 Q4")
names(exchange_rate_usd) <- "ERA"

exchange_p = autoplot(exchange_rate_usd) +
  theme_classic()+
  scale_x_yearqtr(format = "%Y")+
  labs(title = "Exchange Rate (AUD/USD)")+
  theme(axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5,
                                  face = "bold"))

```

```{r}
#| echo: false
#| message: false
#MB Monetary base, seasonally adjusted (M1)
MB <- read_rba(series_id = "DMAM1S") 
MB = xts(MB$value, order.by = MB$date)   
MB = to.quarterly(MB,OHLC = FALSE)
MB <- window(MB,                   
               start = "1980 Q1",
               end = "2022 Q4")
MB = log(MB)
names(MB) <- "MB"
MB_p = autoplot(MB) +
  theme_classic()+
  scale_x_yearqtr(format = "%Y")+
  labs(title = "Monetary Base (M1)")+
  theme(axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5,
                                  face = "bold"))

```


```{r}
#| echo: false
#| message: false
Short_R <- read_rba(series_id = "FIRMMBAB90") 
Short_R = xts(Short_R$value, order.by = Short_R$date)    
Short_R = to.quarterly(Short_R,OHLC = FALSE)
Short_R <- window(Short_R,                   
             start = "1980 Q1",
             end = "2022 Q4")
Short_R = log(Short_R)
names(Short_R) <- "Short_R"
SR_p = autoplot(Short_R) +
  theme_classic()+
  scale_x_yearqtr(format = "%Y")+
  labs(title = "Short-Term Interest Rate")+
  theme(axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5,
                                  face = "bold"))

```


```{r}
#| echo: false
#| message: false
#CPI Consumer price index, seasonally adjusted

CPI = read_abs(series_id = 'A2325846C')
CPI = xts(CPI$value, order.by = CPI$date)    
CPI <- window(CPI,                   
                  start = "1980-03-01",
                  end = "2022-12-01")
CPI = log(CPI)
names(CPI) <- "CPI"
CPI_p = autoplot(CPI) +
  theme_classic()+
  labs(title = "Consumer Price Index")+
  theme(axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5,
                                  face = "bold"))

```


```{r}
#| echo: false
#| message: false
GDP = read_rba(series_id = "GGDPCVGDP")
GDP = xts(GDP$value, order.by = GDP$date)    
GDP <- window(GDP,                   
              start = "1980-03-31",
              end = "2022-12-31")
GDP = log(GDP)
names(GDP) <- "GDP"
GDP_p = autoplot(GDP) +
  theme_classic()+
  labs(title = "Gross Domestic Product")+
  theme(axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5,
                                  face = "bold"))


```


```{r}
#| echo: false
#| message: false
#| 
#combining 


exchange_p + MB_p + SR_p + GDP_p  + CPI_p  + plot_layout(ncol = 2)
```


```{r}
#| echo: false
#| message: false
data_all = list(exchange_rate_usd, MB, Short_R, GDP, CPI)
variable <- c('ERA', 'MB', 'Short_R','GDP', 'CPI')
N <- rep(172, length(variable))
mean <- sapply(data_all, mean)
sd <- sapply(data_all, sd)
Min <- sapply(data_all, min)
Max <- sapply(data_all, max)
table1 =data.frame(variable, N, mean,sd, Min, Max)


knitr::kable(table1, caption = "Summary Statistics", digits = 2)
```

> **ACF plots.**

```{r}

#| echo: false
#| message: false
par(mfrow = c(3, 2))
acf(exchange_rate_usd, lag.max = 10, plot = TRUE) 
acf(MB, lag.max = 10, plot = TRUE) 
acf(Short_R, lag.max = 10, plot = TRUE) 
acf(GDP, lag.max = 10, plot = TRUE) 
acf(CPI, lag.max = 10, plot = TRUE) 
```

> **PACF plots.**

```{r}
#| echo: false
#| message: false
par(mfrow = c(3, 2))
pacf(exchange_rate_usd, lag.max = 10, plot = TRUE) 
pacf(MB, lag.max = 10, plot = TRUE) 
pacf(Short_R, lag.max = 10, plot = TRUE) 
pacf(GDP, lag.max = 10, plot = TRUE) 
pacf(CPI, lag.max = 10, plot = TRUE) 
```

## A Simple Example

```
## References {.unnumbered}